On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-10-08 docs/mvfits_paper/mvf.tex
Update Methods intro with Marks comments
Update Methods::A with Marks comments

The central player is \eqn{lin1} is the set of basis coefficients $\mu_{k}$.

@@

  \hatP = \left( \left( \hatU^{-1} \right)^T \hatU^{-1} \right)^{-1}

@@

The the trial model with smallest representation error is kept for the next greedy iteration.

@@

  \caption{A positive (forward) greedy algorithm, \pgreedy{}, \texttt{PGREEDY}. Note that a required input, $\mathcal{A}$, is a function that takes in a list of basis symbols, and outputs an estimator of fit error. In this setting, $\mathcal{A}$ is assumed to have access to peripheral information, such as the training data.}

>>>>

The central player in \eqn{lin1} is the set of basis coefficients $\mu_{k}$.

@@

  \hatP = \left( \hatU^{*} \hatU \right)^{-1}\hatU^{*}

@@

The trial model with smallest representation error is kept for the next greedy iteration.

@@

  \caption{A positive (forward) greedy algorithm, \pgreedy{}. Note that a required input, $\mathcal{A}$, is a function that takes in a list of basis symbols, and outputs an estimator of fit error. In this setting, $\mathcal{A}$ is assumed to have access to peripheral information, such as the training data.}
